Statistical performance analysis of data-driven neural mass models

### 2013-08-22 manuscript/manuscript.tex
Manuscript and MATLAB code

\begin{figure}[ht]
  \begin{center}
    \includegraphics{./figures/pdf/AlphaSeizureBar}
  \end{center}
  \caption{The BCRB for two models in alpha and seizure states}
  \label{fig:CrbBar}
\end{figure}

@@

Fig.~\ref{sdf} illustrates that the seizure type behaviour is easier to estimate than background alpha rhythms...<text here>. This is perhaps not surprising since, intuitively, seizure oscillations appear more structured and have larger amplitudes as illustrated in Fig.~\ref{fig:NMMs}.

@@

Table here

>>>>

\begin{figure}[ht]
  \begin{center}
    \includegraphics{./figures/pdf/AlphaSeizureBar}
  \end{center}
  \caption{The BCRB for two models in alpha and seizure states}
  \label{fig:AlphaSeizure}
\end{figure}

@@

Fig.~\ref{fig:AlphaSeizure} illustrates that the states underlying seizure type behaviour is more difficult to estimate than background alpha rhythms. This is expected since the input noise driving the system is amplified by a larger synaptic gain parameter, $A$, for the seizure state, as listed in Table~\ref{tbl:Parameters}. This increases the overall uncertainty in the model, reduces the information obtained by the measurements and thus increases the bound.

@@

Table here
\begin{table}

	\caption{\label{tbl:Parameters}Parameters used to generate different states}
\end{table}
